\documentclass[14pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[english,russian]{babel}

\usepackage{graphicx}
\usepackage{mathtools,amssymb}
\usepackage{amsmath}

\usepackage{hyperref}

\usepackage{subcaption}
% Generate dummy text
\usepackage{lipsum}  
\usepackage{array,multirow}

\def \adl {adl/}

\begin{document}

	Математическая модель:
\begin{equation}\label{mm}
	\beta V_p\frac{\partial p}{\partial t} = q + \sum_{i=1}^{N}T_i\left(p-p_i\right)
\end{equation}

\begin{equation}\label{mm1}
	\beta V_p\frac{p^{n+1} - p^n}{\Delta t} = q^{n+1} + \sum_{i=1}^{N}T_i\left(p_i^{n+1}-p^{n+1}\right) + T_a\left(p_a - p^{n+1}\right)
\end{equation}

\begin{equation}
	q^n = w\left(p^n-p_w^n\right)
\end{equation}

\begin{equation}
	p^n = \frac{1}{w}q^n + p_w^n = w^*q^n + p_w^n
\end{equation}

\begin{equation}
	\beta V_p \left(p^{n+1} - p^n\right) = q^{n+1}\Delta t + \sum_{i=1}^{N}T_i\left(p_i^{n+1}-p^{n+1}\right)\Delta t + T_a\left(p_a - p^{n+1}\right)\Delta t
\end{equation}
	
\begin{eqnarray*}\label{mm2}
	\beta V_p \left(p_w^{n+1} - p_w^n\right) + \beta V_p w\left(q^{n+1} - q^n\right) = \\
	= q^{n+1}\Delta t + \sum_{i=1}^{N} T_i \left({p_w}_i^{n+1}-p_w^{n+1}\right)\Delta t + 
	\sum_{i=1}^{N} T_i \left(w_i q_i^{n+1}-w q^{n+1}\right)\Delta t \\
	+  T_a\left(p_a - p_w^{n+1}\right)\Delta t - T_a w^* q^{n+1}
\end{eqnarray*}
\begin{equation*}
	v^* = \frac{1}{\beta V_p}
\end{equation*}


\begin{eqnarray*}\label{mm3}
 \Delta p_w^{n+1}  = - w\left(q^{n+1} - q^n\right) 
	+ q^{n+1} v^* \Delta t
	+ v^* \sum_{i=1}^{N} T_i \left({p_w}_i^{n+1}-p_w^{n+1}\right)\Delta t + \\
    + v^* \sum_{i=1}^{N} T_i \left(w_i q_i^{n+1}-w q^{n+1}\right)\Delta t 
	+  v^* T_a\left(p_a - p_w^{n+1}\right)\Delta t - v^* T_a w^* q^{n+1}
\end{eqnarray*}

\begin{eqnarray*}\label{mm4}
	p_w^{n+1} - p_w^m  = - w^*\left(q^{n+1} - q^m\right) 
	+ \sum_{\tau=m+1}^{n+1}q^\tau v^* \Delta t
	+ v^* \sum_{\tau=m}^{n}\sum_{i=1}^{N} T_i \left({p_w}_i^\tau-p_w^\tau\right)\Delta t + \\
	+ v^*  \sum_{\tau=m}^{n} \sum_{i=1}^{N} T_i \left(w^*_i q_i^\tau-w^* q^\tau\right)\Delta t 
	+  \sum_{\tau=m}^{n} v^* T_a\left(p_a - p_w^\tau\right)\Delta t - v^* T_a w^*  \sum_{\tau=m}^{n} q^\tau \Delta t
\end{eqnarray*}



	$p$ - пластовое давление;
	
	$p_w$ - забойное давление;
	
	$q_m$ - массовый расход;
	
	$\sigma = \sigma(x,y)$ - гидропроводность;
	
	$\kappa_j$ - коэффициент связи с пластом для j-той скважины;
	
	$\lambda$ - продуктивность контура питания (аквифера).
	
	$m$ - пористость.
	
	$h$ - эффективная толщина.
	
	
	\begin{thebibliography}{20}
		
		\bibitem{raf} R. Holanda, "A State-of-the-Art Literature Review on Capacitance
		Resistance Models for Reservoir Characterization
		and Performance Forecasting" Rafael Wanderley de Holanda, Eduardo Gildin, Jerry L. Jensen, Larry W. Lake and C. Shah Kabir. Energies 2018, 11(12), 3368; https://doi.org/10.3390/en11123368
		
		\bibitem{kos} V. P. Kosyakov, "Structural and Parametric Identification
		of an Aquifer Model for an Oil Reservoir". Lobachevskii J. Math.
		{\bf 41}, 1242--1247 (2020).
		
		\bibitem{bas} K. S. Basniev, N. M. Dmitriev, R. D. Kanevskaya, and V. M. Maksimov,
		\textit{Underground hydromechanics}. M.-Izhevsk: Institute for
		Computer Research, 2006 [in Russian].
		
		\bibitem{azi} H. Aziz and E. Settari, \textit{Mathematical modeling of reservoir systems}.
		M.-Izhevsk: Institute for Computer Research, 2004 [in Russian].
		
		\bibitem{opt} V. P. Kosyakov and S. P. Rodionov, "Optimal control of wells on the basis
		of two-phase filtration equations", Proceedings of MIPT {\bf 8} (3),
		79--90 (2016).
		
		\bibitem{leg} V. P. Kosyakov and  D. Yu. Legostaev, "Using elements of machine learning to
		solve the inverse problem of reconstructing the hydraulic 
		conductivity feld for a fltration problem", Tyumen State University
		Herald. Physical and Mathematical Modeling. Oil, Gas, Energy {\bf 8}
		(2 (30)), 129--149.
		
	\end{thebibliography}
	
\end{document}
